%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Learning Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Main Programmer \& Group Leader} % Job title
    {Introduction to Biomedical Informatics (IBI) 1 Group Project} % Organization
    {Haining, P.R.China} % Location
    {Mar. 2025 - Apr. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked with 3 group mates.}
        \item {Developed programs to count the most frequent codon(s) in the given DNA sequences, interpret the codon(s) into amino acid(s), and calculate amino acid frequencies.}
        \item {Extended the program functionality to perform simple alignment of two DNA sequences and calculate the similarity score based on global alignment.}
        \item {Implemented the above programs in Python.}
        \item {Created a poster and gave a presentation on the project.}
        \item {The code package can be found in the IBI1\_ICA repository on my GitHub.}
      \end{cvitems}
    }

%---------------------------------------------------------
 \cventry
    {Participant} % Job title
    {Introduction to Biomedical Informatics (IBI) 1 Practical} % Organization
    {Haining, P.R.China} % Location
    {Feb. 2025 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Studied the basics of bioinformatics and programming skills in Python.}
        \item {Developed several programs, including manipulating FASTA profiles, calculating TATA boxes, and simulating virus outbreaks among vaccinated populations.}
        \item {Gained proficiency in using Linux and remote servers.}
        \item {Built a GitHub account and personal portfolio.}
        \item {All outcomes can be found in the IBI1\_2024\text{-}25 repository on my GitHub.}
        \item {My personal portfolio can be found at \underline{\url{https://shwenyu.github.io/}}.}
      \end{cvitems}
      }

%---------------------------------------------------------
  \cventry
    {Group Leader} % Job title
    {Introduction to Cellular and Molecular Biology (ICMB) 1 Group Wiki Project} % Organization
    {Haining, P.R.China} % Location
    {Feb. 2025 - Mar. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Collaborated with 5 students to create a wiki page introducing the overall knowledge of CRFR1 in the human body.}
        \item {Authored the section on the structure of CRFR1, including its unique secondary structure with a binding knot and its function-related structural specificity.}
        \item {Formatted and organized the wiki page.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
\end{cventries}
